RUPEE: A fast and accurate purely geometric protein structure search

### 2018-11-16 docs/S1_benchmarks.tex
supporting info

\documentclass[letter,center,fleqn]{NAR}

\usepackage{textcomp}
\usepackage{lmodern}
\usepackage{gensymb}
\usepackage{booktabs}

@@

\onecolumn
\section{FIGURES}

\begin{figure*}[h!]
\begin{center}
\includegraphics{combined_scoring_fatcat}
\end{center}
\caption{Scoring from FATCAT pairwise alignments for RUPEE fast, RUPEE top-aligned sorted by TM-Score, and RUPEE top-aligned sorted by RMSD}
\label{fig:combined_scoring_fatcat}
\end{figure*}

\newpage

\section{METHODS ADDENDUM}

To see why RPE run factors are calculated at the descriptor level and factored in at the shingle level, consider shingling a list of RPE run factors themselves, which mirrors applying them at the descriptor level. 
\begin{align*}
    &\text{The sequence of RPE factors} \\
    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 1, 2, 3], [1, 2, 3, 2], [2, 3, 2, 1], [3, 2, 1, 0] \,\} \\
    &\text{and with one less element} \\
    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 1, 2, 2], [1, 2, 2, 1], [2, 2, 1, 0] \,\}
\end{align*}
Notice above, there is not a single match for this one-off difference in run length.
Now consider shingling a list of RPE factors, but this time all elements in the shingle are set equal to the first element in the shingle, which mirrors applying them at the shingle level. 
\begin{align*}
    &\text{The sequence of RPE factors} \\
    &\qquad[\, 0, 1, 2, 3, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2], [3, 3, 3, 3] \,\} \\
    &\text{and with one less element} \\
    &\qquad[\, 0, 1, 2, 2, 1, 0 \,] \text{ becomes} \\
    &\qquad\{\, [0, 0, 0, 0], [1, 1, 1, 1], [2, 2, 2, 2] \,\}
\end{align*}
In this latter case, a one-off difference in run length results in one less shingle match while still serving to increase the specificity of the shingles.

\newpage
\section{BENCHMARKS}

>>>>

\documentclass[letter]{article}

\usepackage{lmodern}

@@

\section{Benchmarks}

### 2018-11-16 docs/rupee.tex
supporting info

All benchmark definitions can be found in \nameref{S3_Benchmarks}.

@@

A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S1_Fig}. 
The same relative relationships hold with only small variations.

@@

\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Scoring from FATCAT pairwise alignments.}

\paragraph*{S2 Methods.}
\label{S2_Methods}
{\bf Run factors for shingles instead of descriptors.}

\paragraph*{S3 Benchmarks.}
\label{S3_Benchmarks}
{\bf Domains included in benchmarks used for evaluation.}

>>>>

All benchmark definitions can be found in \nameref{S1_Benchmarks}.

@@

A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S2_Fig}. 
The same relative relationships hold with only small variations.

@@

\paragraph*{S1 Benchmarks.}
\label{S1_Benchmarks}
{\bf Domains included in benchmarks used for evaluation.}

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Scoring from FATCAT pairwise alignments.}

\paragraph*{S3 Methods Addendum.}
\label{S3_Methods}
{\bf Run factors for shingles instead of descriptors.}
